Supplementary materials: Reproducibility of SNV-calling in multiple sequencing runs from single tumors

### 2015-11-23 PAPER/Supplementary.tex
finished editing legends in Supplementary.tex

%% Figure 2
\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS1.pdf} }
\caption{\textbf{One third (WGA) to one half (WGS) of putative SNVs were recovered in technical replicates.} Density of the percentage of each WGS (green) and WGA (orange) sample that is present in the overlap between replicates for each patient. The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter.}
\label{fig:density}
\end{figure}

\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS2.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with coverage.} The number of SNVs called in a sample does not correlate with the coverage of that sample  (Spearman $\rho=-0.13$, $S=671817$, $P=0.12$). While at first glance, it appears that there may be significant separation between WGS and WGA samples along the $y$-axis (WGA samples lie above and below WGS samples), this is not the case because the $y$-axis value (coverage) is an experimental and not a test parameter. It does not impact our results.} 
\label{fig:coverage}
\end{figure}

\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS3.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with percentage of mapped reads.} The number of SNVs called in a sample does not correlate with the percentage of mapped reads in the alignment of that sample  (Spearman $\rho=-0.068$, $S=637326$, $P=0.41$).} 
\label{fig:percent_mapped}
\end{figure}

@@

%% Data processing commands table
\begin{landscape}
\begin{table}
\caption{\textbf{Back-end Processing.} This table shows the software packages we used in data processing, what we used each piece of software for, and the command associated with it. The rows are in order of use.}
\label{tab:commands}
\begin{tabular}{ p{2.5cm} p{6cm} p{12cm} }
	software & purpose & command\\
	\hline
	picard & regenerate fastq files from BAM file aligned to hg18 & \texttt{java -d64 -Xmx4g -jar SamToFastq.jar I=\$pfx.bam F=\$pfx.1.fastq F2=\$pfx.2.fastq 2$>$\&1} \\
	bwa & align fastq files to hg19 & \texttt{bwa aln -q 30 -t 8 \$hgReference \$fastq $>$ \$fastq.aln.sai} \\
	bwa, samtools & convert aligned fastq files into new BAM file & \texttt{bwa sampe -a 600 -P -r "\$RG" \$hgReference \$fastq1.aln.sai \$fastq2.aln.sai \$fastq1 \$fastq2 | samtools view -bSh -o \$outprefix.bam -} \\
	samtools & sort and index new BAM file & \texttt{samtools sort -@ 16 \$outprefix.bam \$outprefix.sorted 2, samtools index \$outprefix.sorted.bam 2} \\
	samtools & remove duplicate reads from BAM files & \texttt{samtools rmdup ../\$tumorpfx/\$tumorpfx.out.sorted.bam \$tumorpfx.dedup.bam} \\
	GATK & indel realignment & \texttt{java -d64 -jar \$gatkJar -R \$hgReference -T IndelRealigner -rf BadCigar -I \$tumorpfx.dedup.bam -known \$G1000.Mills -known \$G1000.Phase1.Indels -targetIntervals \$tumorpfx.intervals -o \$tumorpfx.realn.bam} \\
	GATK & base recalibration & \texttt{java -d64 -jar \$gatkJar -nct 8 -T BaseRecalibrator -rf BadCigar -I \$tumorpfx.realn.bam -R \$hgReference -knownSites \$dbSNP -o \$tumorpfx.recal.grp} \\
	samtools & index recalibrated BAM file & \texttt{samtools index \$tumorpfx.realn.recal.bam} \\
	SomaticSniper & call somatic mutations, generate VCF & \texttt{bam-somaticsniper -q 40 -Q 40 -J -s 0.001 -F vcf -f \$hgReference \$tumorbam \$normalbam \$tumorpfx.SS.vcf} \\
\end{tabular}
\end{table}
\end{landscape}

>>>>

%% Figure S1
\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS1.pdf} }
\caption{\textbf{One third (WGA) to one half (WGS) of putative SNVs were recovered in technical replicates.} For each pair of replicates (WGS and WGA), we looked at the percentage of WGS SNVs that were recovered in the WGA sample (about one half, in green), and the percentage of the WGA SNVs that were recovered in the WGS sample (about one third, in orange). The WGS distribution is higher and narrower, showing that the WGS samples overall have a higher percentage overlap than the WGA samples, and less range in this parameter.}
\label{fig:density}
\end{figure}

%% Figure S2
\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS2.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with coverage.} The number of SNVs called in a sample does not correlate with the coverage of that sample  (Spearman $\rho=-0.13$, $S=671817$, $P=0.12$). This is shown by the consistent variability along the $x$-axis at each level of overage (shown on the $y$-axis). The separation of the two experimental condition on the $y$-axis is not relevant to this measure.} 
\label{fig:coverage}
\end{figure}

%% Figure S3
\begin{figure}
\centerline{
\includegraphics[width=5in]{FigureS3.pdf} }
\caption{\textbf{Number of putative SNVs in a sample does not correlate with percentage of mapped reads.} The number of SNVs called in a sample does not correlate with the percentage of mapped reads in the alignment of that sample  (Spearman $\rho=-0.068$, $S=637326$, $P=0.41$).} 
\label{fig:percent_mapped}
\end{figure}

@@

%% Data processing commands table
\begin{landscape}
\begin{table}
\caption{\textbf{Back-end Processing.} This table shows the software packages we used in data processing, what we used each piece of software for, and the command associated with the use of it. The rows are in order of use.}
\label{tab:commands}
\begin{tabular}{ p{2.5cm} p{6cm} p{12cm} }
	software & purpose & command\\
	\hline
	picard & regenerate fastq files from BAM file aligned to hg18 & \texttt{java -d64 -Xmx4g -jar SamToFastq.jar I=\$pfx.bam F=\$pfx.1.fastq F2=\$pfx.2.fastq 2$>$\&1} \\
	bwa & align fastq files to hg19 & \texttt{bwa aln -q 30 -t 8 \$hgReference \$fastq $>$ \$fastq.aln.sai} \\
	bwa, samtools & convert aligned fastq files into new BAM file & \texttt{bwa sampe -a 600 -P -r "\$RG" \$hgReference \$fastq1.aln.sai \$fastq2.aln.sai \$fastq1 \$fastq2 | samtools view -bSh -o \$outprefix.bam -} \\
	samtools & sort and index new BAM file & \texttt{samtools sort -@ 16 \$outprefix.bam \$outprefix.sorted 2, samtools index \$outprefix.sorted.bam 2} \\
	samtools & remove duplicate reads from BAM files & \texttt{samtools rmdup ../\$tumorpfx/\$tumorpfx.out.sorted.bam \$tumorpfx.dedup.bam} \\
	GATK & indel realignment & \texttt{java -d64 -jar \$gatkJar -R \$hgReference -T IndelRealigner -rf BadCigar -I \$tumorpfx.dedup.bam -known \$G1000.Mills -known \$G1000.Phase1.Indels -targetIntervals \$tumorpfx.intervals -o \$tumorpfx.realn.bam} \\
	GATK & base recalibration & \texttt{java -d64 -jar \$gatkJar -nct 8 -T BaseRecalibrator -rf BadCigar -I \$tumorpfx.realn.bam -R \$hgReference -knownSites \$dbSNP -o \$tumorpfx.recal.grp} \\
	samtools & index recalibrated BAM file & \texttt{samtools index \$tumorpfx.realn.recal.bam} \\
	SomaticSniper & call somatic mutations, generate VCF & \texttt{bam-somaticsniper -q 40 -Q 40 -J -s 0.001 -F vcf -f \$hgReference \$tumorbam \$normalbam \$tumorpfx.SS.vcf} \\
\end{tabular}
\end{table}
\end{landscape}
